### 2022-11-29 dissertation/chapters/08-results.tex
✨ (plots): Larger fonts
🚧  (final-review): Chapter 8  - almost done

Given the stochastic nature of the \index{heuristic}heuristic selection mechanism, sufficient samples of the performance of each heuristics-entity combination in the performance log is required for the \acs{BHH} to learn. This requirement is further strengthened by the Bayesian nature of the probabilistic model implemented by the \acs{BHH}. The probabilistic model implements \textit{probabilities of heuristic selection probabilities} and as such, insufficient samples in the performance log could render a form of random search.

@@

      \item \textbf{Section \ref{sec:results:case_study:probs_of_select_probs}} provides illustrations and discussions around the changes in the \textit{probabilities of \index{heuristic}heuristic selection probabilities} as a result of the learning mechanism implemented by the \acs{BHH}.

@@

\subsection{Probabilities of Heuristic Selection Probabilities}\label{sec:results:case_study:probs_of_select_probs}

This section provides a detailed investigation into the \textit{probabilities of \index{heuristic}heuristic selection probabilities}, denoted by $\boldsymbol{\theta}$, as it changes throughout the training process. As a reminder, the \acs{BHH} implements a Bayesian view of probabilistic modeling and thus, \index{heuristic}heuristic selection probabilities are defined by an underlying probablistic distribution themselves. The probability distribution of \index{heuristic}heuristic selection probabilities is denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, and the prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.

Figures~\ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} provide illustrations of the probabilities of \index{heuristic}heuristic selection probabilities, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs. These illustrations are presented in log scale. Indices 0, 6, 7, and 8 represent the probabilities of \index{heuristic}heuristic selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the probabilities of \index{heuristic}heuristic selection probabilities in $\boldsymbol{\theta}$ and thus, the \index{heuristic pool}heuristic pool. Once again, simular illustrations for the other elements in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.

\begin{figure}[htb]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[0].pdf}
            \caption{P($\theta_{0} \vert \alpha_{0})$ - \acs{SGD}}
            \label{fig:results:case_study:thetas:0}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[6].pdf}
            \caption{P($\theta_{6} \vert \alpha_{6})$ - \acs{Adam}}
            \label{fig:results:case_study:thetas:6}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[7].pdf}
            \caption{P($\theta_{7} \vert \alpha_{7})$ - \acs{PSO}}
            \label{fig:results:case_study:thetas:7}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[8].pdf}
            \caption{P($\theta_{8} \vert \alpha_{8})$ - \acs{GA}}
            \label{fig:results:case_study:thetas:8}
      \end{subfigure}
      \par\bigskip
      \caption{The average sampled probabilities of \index{heuristic}heuristic selection probabilities, denoted $\boldsymbol{\theta}$, at indices 0, 6, 7, and 8. The probabilities of \index{heuristic}heuristic selection probabilities are sampled from the probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:thetas}
\end{figure}

From the illustrations presented in Figures~\ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8}, a clearer picture of the learning process of the \acs{BHH} is formed. The first important observation to make is for the bhh\_replay\_250 configuration, presented in \textcolor{green}{green}. As a reminder, ten low-level \index{heuristic}heuristics are included in the heuristic pool, yielding an expected probability of \index{heuristic}heuristics selection probability of 0.1, for each \index{heuristic}heuristic, by the frequentist view of probabilistic modeling.

Towards the end of the training process, the probability of \index{heuristic}heuristic selection probability converges back to the symmetrical, uniform probability distribution, yielding a probability of \index{heuristic}heuristic selection probability of 0.1, for all \index{heuristic}heuristics. This can be explained as follows: most of the training progress is made in the early stages of the training process, and training converges towards the end of the training process. Since training converges, all heuristics, no matter their past performances, fail to yield better solutions towards the end of the training process. As a result of training convergence, heuristics then fail to meet the performance criteria and credit allocations by means of the credit assignment strategy.

@@

Another observation to make occurs in the first 30 steps of the training process. In Figure~\ref{fig:results:case_study:thetas}, notice how all three configurations mostly yield the same probabilities of \index{heuristic}heuristic selection probabilities in these first 30 steps. This can be explained as follows: all three configurations use a different random seed per run, but use the same random seed across configurations for the same run number. This is done so that any difference in the behaviour of the different \acs{BHH} configurations are then not a result of random sampling, but solely because of differences in their approaches. This is especially applicable to the initialisation process, where entities are randomly placed in the search space, as well as the early stages of training, where most of the training progress is made.

@@

Furthermore, the variance of $\boldsymbol{\theta}$, for the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration, with means not equal to the expected probabilities of \index{heuristic}heuristic selection probabilities of 0.1, observed for small windows, at various steps for multiple runs, is proof that the \acs{BHH} does not just implement a form of random search, despite having small reanalysis interval and replay window size configurations. This is also true for the bhh\_credit\_symmetric configuration, as the bhh\_credit\_symmetric configuration biases towards heuristics that happen to be sampled, despite not biasing towards good performance.

Finally, the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration both yield similar volatile behaviour, much more so than with the bhh\_replay\_250 configuration. This can be attributed to a very small reanalysis window combined with a small replay window size of 10, that contains very few samples to learn from. A small reanalysis interval and a small replay window size allows for more exploration of the \index{heuristic}heuristic space, but can also yield greater variance of the probabilities of \index{heuristic}heuristic selection probabilities. Once again, any differences then in the behaviour of the bhh\_baseline compared to the bhh\_credit\_symmetric configurations is proof of small performance exploitations and biases by the bhh\_baseline configuration.

@@

This section provides a brief investigation into the \textit{prior \index{heuristic}heuristic selection probabilities} that result from the probabilistic model implemented by the \acs{BHH}. The prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.

Figures~\ref{fig:results:case_study:p_H:0} to \ref{fig:results:case_study:p_H:8} provide illustrations of the prior \index{heuristic}heuristic selection probabilities, sampled from the \index{heuristic}heuristic selection probability distribution $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8, throughout the training process, and averaged over all 30 runs. Similar to before, these illustrations are also presented in log scale.

\begin{figure}[htb]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[0].pdf}
            \caption{P($h_{0} \vert \theta_{0})$ - \acs{SGD}}
            \label{fig:results:case_study:p_H:0}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[6].pdf}
            \caption{P($h_{6} \vert \theta_{6})$ - \acs{Adam}}
            \label{fig:results:case_study:p_H:6}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[7].pdf}
            \caption{P($h_{7} \vert \theta_{7})$ - \acs{PSO}}
            \label{fig:results:case_study:p_H:7}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[8].pdf}
            \caption{P($h_{8} \vert \theta_{8})$ - \acs{GA}}
            \label{fig:results:case_study:p_H:8}
      \end{subfigure}
      \par\bigskip
      \caption{The average sampled prior \index{heuristic}heuristic selection probabilities, given the probabilities of \index{heuristic}heuristic selection probabilities, denoted by $\boldsymbol{H}$, at indices 0, 6, 7, and 8. The prior \index{heuristic}heuristic selection probabilities are sampled from the prior \index{heuristic}heuristic selection probability distribution, denoted $P(\boldsymbol{H} \vert \theta)$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:p_H}
\end{figure}

The main observation to make from these figures is that they are much less volatile and noisy than the figures presented for the probabilities of \index{heuristic}heuristic selection probabilities presented in the previous section in Figure~\ref{fig:results:case_study:thetas}. This is because of the \textit{reselection} interval hyper-parameter. The reselection interval hyper-parameter is implemented as a way to control the frequency by which new heuristics are selected and allocated to each entity. Since the default \textit{reselection} interval is set to 10, the \index{heuristic}heuristic selection probabilities are only resampled at intervals of 10. These illustrations then simply yield rough approximations of the illustrations provided in Figures~\ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} for the probabilities of \index{heuristic}heuristic selection probabilities. As such, the same observations and conclusions that are made in Section \ref{sec:results:case_study:probs_of_select_probs} also apply in this section.

@@

This section provides a detailed discussion on the outcomes of the \textit{posterior heuristic selection probabilities}. These posterior heuristic selection probabilities form the basis of the probabilistic model implemented by the \acs{BHH}. The posterior \index{heuristic}heuristic selection probability distribution is defined as $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, where $\boldsymbol{E}$ represents the vector of entities in the entity pool, and $\boldsymbol{C}$ represents the generalised vector of credit allocation outcomes as implemented by the credit assignment strategy. Furthermore $\boldsymbol{\theta}$ and $\boldsymbol{\phi}$ represent the probabilities of \index{heuristic}heuristic selection probabilities and probabilities of entity selection probabilities respectively. Finally, $\boldsymbol{\psi}$ represents the generalised form of the probabilities of successful credit allocation probabilities. Since this dissertation implements credit allocation operations that yield discrete, binary outcomes, $\boldsymbol{\psi}$ can be used interchangeably by $\gamma_{0}$ and $\gamma_{1}$, where $\gamma_{0}$ represents the probabilities of failed credit allocation probabilities and $\gamma_{1}$ represents the probabilities of successful credit allocation probabilities.

@@

\begin{figure}[htb]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
            \caption{$P(h_{0} \vert e_{0}, c_{1})$ - \acs{SGD}}
            \label{fig:results:case_study:p_HgEC:0:0}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
            \caption{$P(h_{6} \vert e_{0}, c_{1})$ - \acs{Adam}}
            \label{fig:results:case_study:p_HgEC:0:6}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
            \caption{$P(h_{7} \vert e_{0}, c_{1})$ - \acs{PSO}}
            \label{fig:results:case_study:p_HgEC:0:7}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
            \caption{$P(h_{8} \vert e_{0}, c_{1})$ - \acs{GA}}
            \label{fig:results:case_study:p_HgEC:0:8}
      \end{subfigure}
      \par\bigskip
      \caption{The average proportional posterior \index{heuristic}heuristic selection probabilities for \index{heuristic}heuristics $(\boldsymbol{H})$ at indices 0, 6, 7, and 8, given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy. The proportional posterior \index{heuristic}heuristic selection probabilities are calculated from the probabilistic model, denoted $P(\boldsymbol{H} \vert e_{0}, \gamma_{1})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:p_HgEC:0}
\end{figure}

>>>>

Given the stochastic nature of the \index{heuristic}heuristic selection mechanism, sufficient samples of the performance of each heuristics-entity combination in the performance log is required for the \acs{BHH} to learn. This requirement is further strengthened by the Bayesian nature of the probabilistic model implemented by the \acs{BHH}. The probabilistic model implements \textit{probability distributions of heuristic selection probabilities} and as such, insufficient samples in the performance log could render a form of random search.

@@

      \item \textbf{Section \ref{sec:results:case_study:probs_of_select_probs}} provides illustrations and discussions around the changes in the \textit{probability distribution of \index{heuristic}heuristic selection probabilities} as a result of the learning mechanism implemented by the \acs{BHH}.

@@

\subsection{Probability Distribution of Heuristic Selection Probabilities}\label{sec:results:case_study:probs_of_select_probs}

This section provides a detailed investigation into the \textit{probability distribution of \index{heuristic}heuristic selection probabilities} as it changes throughout the training process. As a reminder, the \acs{BHH} implements a Bayesian view of probabilistic modeling and thus, \index{heuristic}heuristic selection probabilities are defined by an underlying probablistic distribution themselves. The probability distribution of \index{heuristic}heuristic selection probabilities is denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, where $\boldsymbol{\theta} \sim Dir(\boldsymbol{\alpha, K})$ are the sampled heuristic selection probabilities.

Figures~\ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} provide illustrations of the distribution of \index{heuristic}heuristic selection probabilities, $\boldsymbol{\theta}$, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs. These illustrations are presented in log scale. Indices 0, 6, 7, and 8 represent the distribution of \index{heuristic}heuristic selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the distribution of \index{heuristic}heuristic selection probabilities in $\boldsymbol{\theta}$. Similar illustrations for the other elements in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.

\begin{figure}[htb]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[0].pdf}
            \caption{P($\theta_{0} \vert \alpha_{0})$ - \acs{SGD}}
            \label{fig:results:case_study:thetas:0}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[6].pdf}
            \caption{P($\theta_{6} \vert \alpha_{6})$ - \acs{Adam}}
            \label{fig:results:case_study:thetas:6}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[7].pdf}
            \caption{P($\theta_{7} \vert \alpha_{7})$ - \acs{PSO}}
            \label{fig:results:case_study:thetas:7}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[8].pdf}
            \caption{P($\theta_{8} \vert \alpha_{8})$ - \acs{GA}}
            \label{fig:results:case_study:thetas:8}
      \end{subfigure}
      \par\bigskip
      \caption{The average sampled \index{heuristic}heuristic selection probabilities, denoted $\boldsymbol{\theta}$, at indices 0, 6, 7, and 8. The \index{heuristic}heuristic selection probabilities are sampled from the probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:thetas}
\end{figure}

From the illustrations presented in Figures~\ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8}, a clearer picture of the learning process of the \acs{BHH} is formed. The first important observation to make is for the bhh\_replay\_250 configuration, presented in \textcolor{green}{green}. As a reminder, ten low-level \index{heuristic}heuristics are included in the heuristic pool, yielding an expected mean \index{heuristic}heuristics selection probability of 0.1, for each \index{heuristic}heuristic, by the frequentist view of probabilistic modeling.

Towards the end of the training process, the \index{heuristic}heuristic selection probability converges back to the symmetrical, uniform probability distribution, yielding a \index{heuristic}heuristic selection probability of 0.1, for all \index{heuristic}heuristics. This can be explained as follows: most of the training progress is made in the early stages of the training process, and training converges towards the end of the training process. Since training converges, all heuristics, no matter their past performances, fail to yield better solutions towards the end of the training process. As a result of training convergence, heuristics then fail to meet the performance criteria and credit allocations by means of the credit assignment strategy.

@@

Another observation to make occurs in the first 30 steps of the training process. In Figure~\ref{fig:results:case_study:thetas}, notice how all three configurations mostly yield the same \index{heuristic}heuristic selection probabilities in these first 30 steps. This can be explained as follows: all three configurations use a different random seed per run, but use the same random seed across configurations for the same run number. This is done so that any difference in the behaviour of the different \acs{BHH} configurations are then not a result of random sampling, but solely because of differences in their approaches. This is especially applicable to the initialisation process, where entities are randomly placed in the search space, as well as the early stages of training, where most of the training progress is made.

@@

Furthermore, it can be observed for small windows, at various steps for multiple runs, that the variance of $\boldsymbol{\theta}$, for the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration, do not yield means that are equal to the expected \index{heuristic}heuristic selection probabilities of 0.1. This is proof that the \acs{BHH} does not just implement a form of random search, despite having small reanalysis interval and replay window size configurations. This is also true for the bhh\_credit\_symmetric configuration, as the bhh\_credit\_symmetric configuration biases towards heuristics that happen to be sampled, despite not biasing towards good performance.

Finally, the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration both yield similar volatile behaviour, much more so than with the bhh\_replay\_250 configuration. This can be attributed to a very small reanalysis window combined with a small replay window size of 10, that contains very few samples to learn from. A small reanalysis interval and a small replay window size allows for more exploration of the \index{heuristic}heuristic space, but can also yield greater variance of the \index{heuristic}heuristic selection probabilities. Once again, any differences then in the behaviour of the bhh\_baseline compared to the bhh\_credit\_symmetric configurations is proof of small performance exploitations and biases by the bhh\_baseline configuration.

@@

This section provides a brief investigation into the \textit{prior \index{heuristic}heuristic selection probabilities} that result from the probabilistic model implemented by the \acs{BHH}. The prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$. As such, $P(\boldsymbol{H} \vert \boldsymbol{\theta}) = \boldsymbol{\theta}$ and heuristics are initially sampled such that $\boldsymbol{H} \sim Cat(\boldsymbol{\theta})$.

Figures~\ref{fig:results:case_study:p_H:0} to \ref{fig:results:case_study:p_H:8} provide illustrations of the prior \index{heuristic}heuristic selection probabilities, denoted by $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8, throughout the training process, and averaged over all 30 runs. Similar to before, these illustrations are also presented in log scale.

\begin{figure}[htb]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[0].pdf}
            \caption{P($h_{0} \vert \theta_{0})$ - \acs{SGD}}
            \label{fig:results:case_study:p_H:0}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[6].pdf}
            \caption{P($h_{6} \vert \theta_{6})$ - \acs{Adam}}
            \label{fig:results:case_study:p_H:6}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[7].pdf}
            \caption{P($h_{7} \vert \theta_{7})$ - \acs{PSO}}
            \label{fig:results:case_study:p_H:7}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[8].pdf}
            \caption{P($h_{8} \vert \theta_{8})$ - \acs{GA}}
            \label{fig:results:case_study:p_H:8}
      \end{subfigure}
      \par\bigskip
      \caption{The average prior \index{heuristic}heuristic selection probabilities, $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8. The prior \index{heuristic}heuristic selection probabilities are sampled from the probability distribution of \index{heuristic}heuristic selection probabilities, denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:p_H}
\end{figure}

The main observation to make from these figures is that they are much less volatile and noisy than the figures presented for the distribution of \index{heuristic}heuristic selection probabilities, $\boldsymbol{\theta}$, presented in the previous section in Figure~\ref{fig:results:case_study:thetas}. This is because of the \textit{reselection} interval hyper-parameter. The reselection interval hyper-parameter is implemented as a way to control the frequency by which new heuristics are selected and allocated to each entity. Since the default \textit{reselection} interval is set to 10, the \index{heuristic}heuristic selection probabilities are only resampled at intervals of 10. These illustrations then simply yield rough approximations of the illustrations provided in Figures~\ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} for the distribution of \index{heuristic}heuristic selection probabilities. As such, the same observations and conclusions that are made in Section \ref{sec:results:case_study:probs_of_select_probs} also apply in this section.

@@

This section provides a detailed discussion on the outcomes of the \textit{posterior heuristic selection probabilities}. These posterior heuristic selection probabilities form the basis of the probabilistic model implemented by the \acs{BHH}. The posterior \index{heuristic}heuristic selection probability distribution is defined as $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, where $\boldsymbol{E}$ represents the vector of entities in the entity pool, and $\boldsymbol{C}$ represents the vector of credit allocation outcomes as implemented by the credit assignment strategy. Furthermore $\boldsymbol{\theta}$ and $\boldsymbol{\phi}$ represent the probability distributions of \index{heuristic}heuristic selection probabilities and the entity selection probabilities respectively. Finally, $\boldsymbol{\psi}$ represents the probability distribution of successful credit allocation probabilities.

@@

\begin{figure}[htb]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
            \caption{$P(h_{0} \vert e_{0}, c_{1})$ - \acs{SGD}}
            \label{fig:results:case_study:p_HgEC:0:0}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
            \caption{$P(h_{6} \vert e_{0}, c_{1})$ - \acs{Adam}}
            \label{fig:results:case_study:p_HgEC:0:6}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
            \caption{$P(h_{7} \vert e_{0}, c_{1})$ - \acs{PSO}}
            \label{fig:results:case_study:p_HgEC:0:7}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
            \caption{$P(h_{8} \vert e_{0}, c_{1})$ - \acs{GA}}
            \label{fig:results:case_study:p_HgEC:0:8}
      \end{subfigure}
      \par\bigskip
      \caption{The average calculated proportional posterior \index{heuristic}heuristic selection probabilities for \index{heuristic}heuristics $(\boldsymbol{H})$ at indices 0, 6, 7, and 8, given the application to entity $e_{0}$ and requiring a successful credit allocation, ($c_{1}$), from the \textit{ibest} credit assignment strategy. The proportional posterior \index{heuristic}heuristic selection probabilities are calculated from the probabilistic model, denoted $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:p_HgEC:0}
\end{figure}
